---
title: "Quiz #3"
author: "Milica Cudina"
date: "`r Sys.Date()`"
output: pdf_document
---
<!-- The author of this template is Dr. Gordan Zitkovic.-->
<!-- The code chunk below contains some settings that will  -->
<!-- make your R code look better in the output pdf file.  -->
<!-- If you are curious about what each option below does, -->
<!-- go to https://yihui.org/knitr/options/ -->
<!-- If not, feel free to disregard everything ...  -->
```{r echo=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.align="center",
  fig.pos="t",
  fig.width=12,
  strip.white = TRUE
)
```
<!-- ... down to here. -->

## Loading up the Required Packages
```{r}
library(Rlab)
```

# Simulations
## Problem 1. **(2 points)** 
Draw 100 simulated values from Bernoulli(p=0.2). What is the proportion of "successes" in your simulated batch?

*Solution:*
```{r}
success <- rbern(100,0.2)
Results_Table <- as.numeric(success)
Results_Data_Frame <- data.frame(Results_Table)
Results_Data_Frame$Coded_Results<-ifelse(Results_Data_Frame$Results_Table== 1,"Successes","Failures")
tableresults <- table(Results_Data_Frame$Coded_Results)
prop.table(tableresults)
mean(Results_Table == 1)

```

## Problem 2. **(5 points)** 
Draw 1000 simulated values from Binomial(n=100, p=0.2). Plot the histogram of your simulated values.

*Solution:*
```{r}
binomvector <- c()
for (i in 1:1000) {
  sample1 <- rbinom(1,100,0.2)
  binomvector <- c(binomvector,sample1) }

hist(binomvector, 30, xlab = "Value of Simulated Values", main = " Binomial Distribution \n Simulation",col = "lightsalmon")
```

## Problem 3. **(8 points)** 
Consider the following two-step experiment. First you draw a simulated value from a Bernoulli(p=1/3). If the drawn value from the Bernoulli equals $0$, then you draw a simulated value from Binomial(n=50,p=0.5). On the other hand, if the drawn value from the Bernoulli equals $1$, then you draw a simulated value from Binomial(100,0.5). 

You should repeat the above two-step experiment $1000$ times and draw the histogram of the simulated values. 

*Solution:*
```{r}
results <- c()
for (i in 1:1000) {
successtest <- rbinom(1,1,(1/3))
if (successtest == 0) {
  results <- c(results,rbinom(1,50,0.5))
  } else {
  results <- c(results,rbinom(1,100,0.5)) }}

hist(results,60, xlab = "Value of Simulated Values", col= "olivedrab2", main = "Bernoulli and Binomial \n Distribution Simulation")

```

